% ======================================================================
% APPENDIX B
% Insert this AFTER Appendix A. Do not repeat \appendix if it was already
% issued before Appendix A.
% ======================================================================

\chapter{SUPPLEMENTAL SYNTHETIC BENCHMARK DATA ARCHIVE}
\label{app:supplemental-benchmark-data}

\section{Purpose and Scope}

This appendix documents the machine-readable files supporting the Stage~D synthetic benchmark
results reported in Chapters~IV and~V. Appendix~A provides the consolidated implementation and
artifact crosswalk; the present appendix provides the corresponding data-level record. The archive
is descriptive rather than Monte Carlo inferential and does not provide simulation standard
errors, confidence intervals, power estimates, or hypothesis-test quantities.

The verified archive contains 96 scenario records within each retained block (M1, M2, and M3),
288 scenario records across the three blocks, and seven evaluated model labels per scenario.
Accordingly, the long-form Stage~D file contains 2,016 model-by-scenario rows. M1 entered the
top three in 1 of its 96 scenario records, corresponding to a top-three frequency of
\(1/96=0.0104\). M2 and M3 recorded no top-three placements. No model rerun was performed
to create the archived files.

\section{Versioned Repository Location}

The files are maintained in the versioned GitHub release:

\begin{quote}
\url{INSERT_VERSIONED_RELEASE_URL}
\end{quote}

The release tag should be \texttt{dissertation-appendix-b-v1.0}. A fixed release or commit
permalink is used so that the cited archive remains tied to the exact files reviewed with the
dissertation.

\section{File Inventory}

\begin{table}[htbp]
\raggedright
\caption[Machine-readable files in the supplemental benchmark archive]
{Machine-Readable Files in the Supplemental Benchmark Archive}
\label{tab:appendix-b-file-inventory}
\begin{threeparttable}
\small
\renewcommand{\arraystretch}{1.14}
\begin{tabularx}{\textwidth}{@{}L{4.4cm}L{1.5cm}Y@{}}
\toprule
\textbf{File} & \textbf{Rows} & \textbf{Role} \\
\midrule
\texttt{stage\_d\_model\_group\_summary.csv}
& 21
& Final model-by-block summary used to verify the reported Stage~D means and standard
deviations for IBS, \(\mathrm{IBS}_{\mathrm{STD95}}\), pair-sampled concordance, and the
common-grid weighted negative log score. \\

\texttt{stage\_d\_scenario\_level\_metrics.csv}
& 2,016
& Long-form model-by-scenario Stage~D archive containing scenario identifiers, model labels,
validation and test metrics, time grids, Brier-curve fields, configuration fields, and status
information. \\

\texttt{stage\_b\_candidate\_metrics\_sanitized.csv.gz}
& 174,960
& Compressed development-level candidate/run archive retained for provenance. It is not the
direct source for the final Chapter~IV tables. Absolute high-performance-computing account
paths were sanitized; numerical values were retained. \\

\texttt{checksums.sha256}
& ---
& SHA-256 hashes used to verify that downloaded files match the version cited in the
dissertation. \\
\bottomrule
\end{tabularx}
\begin{tablenotes}[flushleft]
\footnotesize
\item \textit{Note}. The two Stage~D files are the primary machine-readable evidence for
Research Questions~1--4. The Stage~B candidate archive is included as supplementary
development provenance and should not be interpreted as an additional independent benchmark.
\end{tablenotes}
\end{threeparttable}
\end{table}

\FloatBarrier

\section{Research-Question Crosswalk}

The model-group summary and scenario-level archive support the research questions as follows.
Research Question~1 is supported by standardized Integrated Brier Score, pair-sampled
concordance, and scenario-rank fields. Research Question~2 is supported by the saved evaluation
time grids and time-dependent Brier-curve fields. Research Question~3 is supported by the
common-grid weighted negative log score fields. Research Question~4 is supported by the
scenario-level metric distributions, mean ranks, top-three frequencies, and operating-condition
identifiers.

The archived files preserve numerical results already reported in the dissertation. They do not
alter the fitted models, reopen model selection, or introduce a new analysis. Their purpose is to
permit direct inspection of the recorded Stage~D evidence and to strengthen the traceability from
the chapter-facing tables and figures to the machine-readable outputs.

\section{Integrity and Data Stewardship}

The release includes SHA-256 checksums so that file integrity can be verified after download.
Only synthetic benchmark metrics and nonrestricted provenance records are included. Patient-level
clinical records, credentials, access tokens, and restricted source data are excluded from the public
repository.
